Report on Certificate Tools

### 2016-10-06 TEX/draft.tex
Need to get some sleep

\section{General}
%TABLE START
\begin{table}[h!]
\centering
\caption{Overwiew General}
\label{my-label}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|}
\hline
                        & \multicolumn{4}{c|}{General}                                                                               \\ \cline{2-5} 
\multirow{-2}{*}{Tools} & Type   & View + info                                        & License & Operating System                   \\ \hline
OpenSSL                 & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{34FF34}Both       \\ \hline
Keytool                 & JKS    & \cellcolor[HTML]{34FF34}{\color[HTML]{000000} Yes} & Public  & \cellcolor[HTML]{34FF34}Both       \\ \hline
GnuPG                   &        &                                                    &         &                                    \\ \hline
Keystore Explorer       & Both   & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{FFC702}Win | OS X \\ \hline
XCA                     & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{34FF34}Both       \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

      \paragraph{Self-signed certificate}
You can generate key pair by itself and then use it for generation of certificate. If you do not generate key in advance there is option to generate new key whilst generating a certificate. To generate a certificate click on Certificates tab and press New Certificate. There are many options for generating a self-signed certificate, under Source tab you choose a signing algorithm (\verb+MD5|SHA1|SHA224|SHA256|SHA384|SHA512|RIPEMD160+). Under Subject tab, you shoose Common Name, Organisation, etc. fields of certificate and also choose private key. If you didn't generate key in advance then you can generate a new private key (\verb+RSA|DSA|EC+). For certificate to be accepted by all operating systems you need to choose \verb+Digital Signature & Key Agreement & Certificate Sign+ under Key usage tab.
%WILL ADD SCREENSHOTS LATER
      \paragraph{Certificate Signing Request}
Certificate Signing Request is generated simmilarly as a certificate itself, only difference is that you go under Certificate signing request tab and press New Request.
      \paragraph{Specify length}
Length of keys is specified during generation of keys.
      \paragraph{Specify algorithm}
Algorithm used for key generation is specified during generation of keys (\verb+RSA|DSA|EC+).
    \subsubsection{Basic constraints}

      \paragraph{Specify Type}
Type of a certificate is chosen under Extensions tab.
      \paragraph{Specify path length}
Path Length is also specified under Extensions tab.
  \subsection{Specifications}

@@

    \subsubsection{Certificate or certificate chain from a file}
Possible by using export option, choosing in which format you want to export it.
    \subsubsection{Private key only}
Exporting of private key only directly is not availiable.
  \subsection{Direct conversion between Java Keystore and PKCS\#12 file}
Conversion between PKCS\#12 and JKS is not possible.
  \subsection{Importing certificates and keys into storage files}

>>>>

\section{General}
%TABLE START
\begin{table}[h!]
\centering
\caption{Overwiew General}
\label{my-label}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{|c|c|c|c|c|}
\hline
                        & \multicolumn{4}{c|}{General}                                                                               \\ \cline{2-5} 
\multirow{-2}{*}{Tools} & Type   & View + info                                        & License & Operating System                   \\ \hline
OpenSSL                 & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{34FF34}Both       \\ \hline
Keytool                 & JKS    & \cellcolor[HTML]{34FF34}{\color[HTML]{000000} Yes} & Public  & \cellcolor[HTML]{34FF34}Both       \\ \hline
GnuPG                   &        &                                                    &         &                                    \\ \hline
Keystore Explorer       & Both   & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{FFC702}Win | OS X \\ \hline
XCA                     & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{34FF34}Both       \\ \hline
GnuTLS                  & PKCS12 & \cellcolor[HTML]{34FF34}Yes                        & Public  & \cellcolor[HTML]{FFC702}LINUX       \\ \hline
\end{tabular}
\end{adjustbox}
\end{table}
%TABLE END

@@

      \paragraph{Self-signed certificate}
You can generate key pair by itself and then use it for generation of certificate. If you do not generate key in advance there is option to generate new key whilst generating a certificate. To generate a certificate click on Certificates tab and press New Certificate. There are many options for generating a self-signed certificate, under Source tab you choose a signing algorithm (\verb+MD5|SHA1|SHA224|SHA256|SHA384|SHA512|RIPEMD160+). What must be changed is default hash function because it is set to SHA-1 which is no longer considered safe. Under Subject tab, you shoose Common Name, Organisation, etc. fields of certificate and also choose private key. If you didn't generate key in advance then you can generate a new private key (\verb+RSA|DSA|EC+). For certificate to be accepted by all operating systems you need to choose \verb+Digital Signature & Key Agreement & Certificate Sign+ under Key usage tab.
\begin{figure}[!ht]
 \caption{Generation of key for new cert}
 \centering
  \includegraphics[width=0.5\textwidth]{../Dependancies/XCA/genKey.jpg}
\end{figure}

\begin{figure}[!ht]
 \caption{Specify use}
 \centering
  \includegraphics[width=0.5\textwidth]{../Dependancies/XCA/genKey_specif.jpg}
\end{figure}

      \paragraph{Certificate Signing Request}
Certificate Signing Request is generated simmilarly as a certificate itself, only difference is that you go under Certificate signing request tab and press New Request.
\begin{figure}[!ht]
 \caption{Generation of CSR}
 \centering
  \includegraphics[width=0.5\textwidth]{../Dependancies/XCA/newCSR.jpg}
\end{figure}

      \paragraph{Specify length}
Length of keys is specified during generation of keys.
      \paragraph{Specify algorithm}
Algorithm used for key generation is specified during generation of keys (\verb+RSA|DSA|EC+).
\begin{figure}[!ht]
 \caption{Specifying of length and algorithm used}
 \centering
  \includegraphics[width=0.5\textwidth]{../Dependancies/XCA/genKeylength.jpg}
\end{figure}

      \paragraph{Specify Type}
Type of a certificate is chosen under Extensions tab.
      \paragraph{Specify path length}
Path Length is also specified under Extensions tab.

\begin{figure}[!ht]
 \caption{Basic constraints, validity and SAN}
 \centering
  \includegraphics[width=0.5\textwidth]{../Dependancies/XCA/BC_ext.png}
\end{figure}

@@

    \subsubsection{Certificate or certificate chain from a file}
Possible by using export option, choosing in which format you want to export it.
    \subsubsection{Private key only}
Exporting of private key only directly is not availiable.
  \subsection{Direct conversion between Java Keystore and PKCS\#12 file}
Conversion between PKCS\#12 and JKS is not possible.
  \subsection{Importing certificates and keys into storage files}
Certificates and keys can be Exported and imported to/from PKCS or PEM type files.

\chapter{GnuTLS}

  \subsection{Type}
GnuTLS works with PKCS\#12 PEM encoded files
  \subsection{View and information}
To view information about certificate use \verb+certtool --certificate-info --infile [file.pem]+ option.
  \subsection{License}
GnuTLS is under Gnu Public License \- free to use commercialy.
